NN_Accel_Heading

### 2024-03-19 Fish Data Analysis/NN_Accel_Heading.qmd
Working through single fish normalization

```{r}
library(MASS)
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
library(viridis)
library(lme4)

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x/ accuracy) * accuracy}

@@

fish_comp_data <- rbind(fish_comp_data,single_comp_data)

@@

min_dist <- 3 #sd*0.5
max_dist <- 100 #sd*1.5

@@

perp_angle_df <- fish_comp_data %>% filter(Angle >= deg2rad(75) & Angle <= deg2rad(105)) %>% filter(Distance >= 2 & Distance <= 100) %>% filter(Flow == "Still Water")

single_fish_df <- perp_angle_df %>% filter(Darkness == "Single" & Ablation == "Single")
LNDN_fish_df <- perp_angle_df %>% filter(Darkness == "Light" & Ablation == "No Ablation")
LYDN_fish_df <- perp_angle_df %>% filter(Darkness == "Light" & Ablation == "Ablated")
LNDY_fish_df <- perp_angle_df %>% filter(Darkness == "Dark" & Ablation == "No Ablation")
LYDY_fish_df <- perp_angle_df %>% filter(Darkness == "Dark" & Ablation == "Ablated")

LNDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDN_fish_df$Fish1_Yaw_Heading_PS)
LYDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDN_fish_df$Fish1_Yaw_Heading_PS)
LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDY_fish_df$Fish1_Yaw_Heading_PS)
LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDY_fish_df$Fish1_Yaw_Heading_PS)

p.adjust(c(LNDN_KS$p.value,LYDN_KS$p.value,LNDY_KS$p.value,LNDY_KS$p.value))

# perp_model <- aov(Fish1_Yaw_Heading_PS ~ Darkness*Ablation, data = perp_angle_df)
# Anova(perp_model)
# TukeyHSD(perp_model)

ggplot(perp_angle_df, aes(x = Flow_Ablation_Darkness, y = Fish1_Yaw_Heading_PS,
                          fill = Flow_Ablation_Darkness, color = Flow_Ablation_Darkness))+
  stat_dots(side = "both", binwidth = unit(0.01, "npc")) +
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color,"red")) +
  theme_classic()+
  ggtitle("Heading per Second, 2 to 100 BL, 75 to 100 Degrees")

@@

fish_data_nn_model <- fish_data_nn_normal %>% filter(Flow == "Still Water") %>% 
                                       mutate(AblationCat = ifelse(Ablation == "Ablated",1,0),
                                              DarknessCat = ifelse(Darkness == "Dark",1,0))

@@

>>>>

```{r}
library(MASS)
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
library(viridis)
library(lme4)
```

```{r}
rad2deg <- function(rad) {(rad * 180) / (pi)}
deg2rad <- function(deg) {(deg * pi) / (180)}
round_any <- function(x, accuracy, f=round){f(x / accuracy) * accuracy}

@@

#fish_comp_data <- rbind(fish_comp_data,single_comp_data)

@@

min_dist <- 0.5 #sd*0.5
max_dist <- 3 #sd*1.5

offset <- 1.5

top_edge <- 3 - offset 
bottom_edge <- 0# + offset
left_edge <- 0 + offset
right_edge <- 7 - offset

@@

perp_angle_df <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(80) & Mean_Angle <= deg2rad(100)) %>% filter(Flow == "Still Water")#%>% filter(Distance >= 0 & Distance <= 3) %>% filter(Flow == "Still Water")

perp_angle_df_neg <- fish_data_nn_normal %>% filter(Mean_Angle >= deg2rad(-100) & Mean_Angle <= deg2rad(-80)) %>% filter(Flow == "Still Water") %>% mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)

perp_angle_df <- rbind(perp_angle_df,perp_angle_df_neg)

perp_angle_df <- perp_angle_df %>% group_by(Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                                mutate(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                       sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                       n = n()) %>%
                                                ungroup()

#single_fish_df <- perp_angle_df %>% filter(Darkness == "Single" & Ablation == "Single")
LNDN_fish_df <- perp_angle_df %>% filter(Darkness == "Light" & Ablation == "No Ablation")
LYDN_fish_df <- perp_angle_df %>% filter(Darkness == "Light" & Ablation == "Ablated")
LNDY_fish_df <- perp_angle_df %>% filter(Darkness == "Dark" & Ablation == "No Ablation")
LYDY_fish_df <- perp_angle_df %>% filter(Darkness == "Dark" & Ablation == "Ablated")

# LNDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDN_fish_df$Fish1_Yaw_Heading_PS)
# LYDN_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDN_fish_df$Fish1_Yaw_Heading_PS)
# LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LNDY_fish_df$Fish1_Yaw_Heading_PS)
# LNDY_KS <- ks.test(single_fish_df$Fish1_Yaw_Heading_PS,LYDY_fish_df$Fish1_Yaw_Heading_PS)

#p.adjust(c(LNDN_KS$p.value,LYDN_KS$p.value,LNDY_KS$p.value,LNDY_KS$p.value))

perp_model <- aov(Fish1_Yaw_Heading_PS ~ Darkness*Ablation, data = perp_angle_df)
Anova(perp_model)
qqnorm(resid(perp_model))
TukeyHSD(perp_model)

ggplot(perp_angle_df, aes(x = interaction(Ablation, Darkness, sep =", "), y = rad2deg(Fish1_Yaw_Heading_PS),
                          fill = interaction(Ablation, Darkness, sep =", "), color = interaction(Ablation, Darkness, sep =", ")))+
  stat_dots(side = "both", binwidth = unit(0.01, "npc")) +
  geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
  geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
  theme_classic()+
  ggtitle(paste0("All Neighbors From ",min_dist," to ",max_dist))+
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color))

@@

fish_data_nn_model <- fish_data_nn_normal %>% filter(Flow == "Still Water") %>% 
                                       mutate(AblationCat = ifelse(Ablation == "Ablated",1,0),
                                              DarknessCat = ifelse(Darkness == "Dark",1,0)) %>% na.omit()

@@

When are single fish flat?
```{r}

offset <- 2

top_edge <- 3 - offset 
bottom_edge <- 0# + offset
left_edge <- 0 + offset
right_edge <- 7 - offset

#calculate average angle to all other fish in that range
single_fish_mean_angles <- single_comp_data %>%   #filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light") %>%
                                                filter(Fish1_X >= left_edge & Fish1_X <= right_edge) %>%
                                                filter(Fish1_Y >= bottom_edge & Fish1_Y <= top_edge) %>%
                                                #filter(Distance >= min_dist & Distance <= max_dist) %>%
                                                group_by(Date,Year,Month,Day,Trial,
                                                          Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
                                                 summarise(Mean_Angle = rad_ang_mean(Angle),
                                                           #Should be the same number each time
                                                           Fish1_Yaw_Heading_PS = mean(Fish1_Yaw_Heading_PS, rm.na = T),
                                                           Fish1_X = mean(Fish1_X, rm.na = T),
                                                           Fish1_Y = mean(Fish1_Y, rm.na = T)) %>%
                                                 ungroup() %>%
                                                 #normalize
                                                 mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T))

single_flat_lm <- lm(Fish1_Yaw_Heading_PS ~ 1, data = single_fish_mean_angles)
single_lin_lm <- lm(Fish1_Yaw_Heading_PS ~ Mean_Angle, data = single_fish_mean_angles)
single_sin_lm <- lm(Fish1_Yaw_Heading_PS ~ sin(Mean_Angle), data = single_fish_mean_angles)

AIC(single_flat_lm,single_lin_lm,single_sin_lm) %>% arrange(AIC)

single_perp_angle_df <- single_fish_mean_angles %>% filter(Mean_Angle >= deg2rad(80) & Mean_Angle <= deg2rad(100)) %>% filter(Flow == "Still Water")

single_perp_angle_df_neg <- single_fish_mean_angles %>% filter(Mean_Angle >= deg2rad(-100) & Mean_Angle <= deg2rad(-80)) %>% filter(Flow == "Still Water") %>% mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)

single_perp_angle_df <- rbind(single_perp_angle_df,single_perp_angle_df)

t.test(single_perp_angle_df$Fish1_Yaw_Heading_PS)

effect_size <- mean(single_perp_angle_df$Fish1_Yaw_Heading_PS) / sd(single_perp_angle_df$Fish1_Yaw_Heading_PS)

ggplot(single_perp_angle_df, aes(x = Fish1_Yaw_Heading_PS))+
  geom_histogram(color = "black", fill = "red")+
  theme_classic()

ggplot(single_fish_mean_angles, aes(x = Mean_Angle, y = Fish1_Yaw_Heading_PS))+
  geom_point(color = "red")+
  # geom_smooth(method = "glm", formula = y ~ 1, color = "black")+
  # geom_smooth(method = "glm", formula = y ~ x, color = "green")+
  # geom_smooth(method = "glm", formula = y ~ sin(x), color = "blue")+
  theme_classic()

single_fish_mean_angles_heatmap <- single_fish_mean_angles %>% mutate(RoundX = round_any(Fish1_X, -0.5),
                                                                      RoundY = round_any(Fish1_Y, -0.5)) %>%
                                                               group_by(RoundX,RoundY) %>%
                                                               summarise(mean_turn = mean(Mean_Angle)) %>%
                                                               ungroup()

ggplot(single_fish_mean_angles_heatmap, aes(x = RoundX, y = RoundY, fill = mean_turn))+
  geom_tile()+
  coord_equal()+
  scale_fill_gradient2(low = "blue", mid = "white", high = "red")+
  theme_classic()
